Supplementary materials for ``Inattentive responding can induce spurious associations between task behavior and symptom measures''

### 2023-04-03 manuscripts/supp.tex
checkpointing manuscript progress

% load packages
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{xr-hyper} % for cross-referencing between documents
\usepackage{hyperref}
\usepackage{float}
\usepackage{amsmath}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[flushmargin]{footmisc}
\usepackage[flushleft]{threeparttable}
\usepackage{array}
\usepackage[font=small, labelfont=it]{caption}
\usepackage{booktabs}
\usepackage{xcolor,soul}

@@

\begin{figure}[h]
    \includegraphics[width=17cm]{../figures/supp_01.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons). Black Xs indicate significant correlations ablated under screening. No Screening = no exclusions; Accuracy Only = exclusions based on chance-level performance in the reversal-learning task; Infrequency Only = exclusions based on invalid or improbable responses to infrequency items; Both Types = exclusions based on the previous two measures. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
    \label{fig:correlations_s1}
\end{figure}

\clearpage
\subsection*{Bootstrapping Analysis}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_02.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{The pattern of significant behavior-symptom correlations before (panel A) and after (panel B) screening compared to the resulting pattern when random subsets of participants (22\% of total, matched to screening using the infrequency measure) are removed (panel C). Panels A and B are reproduced from Figure \ref{fig:correlations} for convenience. Panel C: the fraction of significant correlations in 5000 bootstrapped samples. Panel D: The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure. Similarity was calculated using the simple matching coefficient. Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]).}
    \label{fig:random}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and false positive rates generalize to other sets of variables}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_03.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{False positive rates for spurious correlations \emph{increase} with sample size. \textit{Left:} Bootstrapped Spearman correlations between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. The grey error bars indicate 95\% bootstrap confidence intervals. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} False positive rates for inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\beta$ and 7-down was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:bootstrap_s1}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and true positive rates for true correlations}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_04.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{True correlations are independent of the proportion of C/IE participants in the sample. \textit{Left:} Bootstrapped Spearman correlations between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. The grey error bars indicate 95\% bootstrap confidence intervals. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} True positive rates for learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. True positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and GAD-7 was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:bootstrap_s2}
\end{figure}

@@

\subsection*{Posterior predictive checks}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_05.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model. \textit{Panel A:} Observed (black) and predicted (blue) learning curves averaged across the group. \textit{Panel B:} Observed versus predicted choice accuracy for each participant. \textit{Panel C:} Distribution of average predictive density across participants.}
    \label{fig:posterior_check}
\end{figure}

@@

\clearpage
\subsection*{Careless participants show different behaviors on the reversal learning task}
\begin{table}[H]
    \centering
    \begin{tabular}{lrrr}
    \toprule
    {} &  Attentive &    C/IE &   $t$-value \\
    \midrule
    Acc      &      0.587 &   0.532 &  $4.008^*$  \\
    Pts      &     50.163 &  47.729 &  $2.376^*$  \\
    WS       &      0.898 &   0.776 &  $5.387^*$  \\
    LS       &      0.609 &   0.751 &  $-5.335^*$ \\
    Pers     &      0.245 &   0.259 &  $-1.505$ \ \\
    $\beta$  &      6.754 &   4.082 &  $5.404^*$  \\
    $\eta_p$ &      0.643 &   0.551 &  $2.846^*$  \\
    $\eta_n$ &      0.738 &   0.784 & $-1.516$ \  \\
    $\kappa$ &     -0.069 &  -0.218 &  $3.729^*$  \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Measures of task behavior compared between attentive and C/IE participants. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

@@

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccccc}
    \toprule
    {} &      INF &      ISD &      REL &      MAH &    READ &     VAR &     ACC &   WSLS & RT \\
    \midrule
    INF  &        - &          &          &          &         &         &         &        &    \\
    ISD  &   0.372* &        - &          &          &         &         &         &        &    \\
    REL  &  -0.408* &  -0.811* &        - &          &         &         &         &        &    \\
    MAH  &   0.406* &   0.843* &  -0.643* &        - &         &         &         &        &    \\
    READ &   -0.111 &   0.193* &  -0.168* &    0.138 &       - &         &         &        &    \\
    VAR  &   -0.061 &   -0.029 &    0.058 &   -0.024 &  -0.026 &       - &         &        &    \\
    ACC  &  -0.206* &   -0.154 &    0.099 &  -0.182* &  -0.074 &   0.027 &       - &        &    \\
    WSLS &    0.060 &    0.102 &   -0.089 &    0.115 &   0.103 &  -0.060 &  0.221* &      - &    \\
    RT   &    0.040 &   -0.019 &    0.014 &    0.013 &  -0.158 &  -0.007 &  -0.094 &  -0.05 &  - \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman's rank correlations of task and self-report data screening measures. Each entry corresponds to the Spearman correlation between two screening measures. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. *Denotes statistical significance after correcting for multiple comparisons.}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccccc}
    \toprule
    {} &     INF &     ISD &     REL &    MAH &   READ &    VAR &     ACC &  WSLS & RT \\
    \midrule
    INF  &       - &         &         &        &        &        &         &       &    \\
    ISD  &  0.462* &       - &         &        &        &        &         &       &    \\
    REL  &  0.484* &  0.691* &       - &        &        &        &         &       &    \\
    MAH  &  0.516* &  0.732* &  0.619* &      - &        &        &         &       &    \\
    READ &   0.319 &   0.165 &   0.165 &  0.216 &      - &        &         &       &    \\
    VAR  &   0.208 &   0.216 &   0.238 &  0.259 &  0.292 &      - &         &       &    \\
    ACC  &  0.379* &   0.312 &   0.258 &  0.344 &  0.237 &  0.282 &       - &       &    \\
    WSLS &   0.253 &   0.247 &   0.227 &  0.258 &  0.299 &  0.303 &  0.505* &     - &    \\
    RT   &   0.267 &   0.219 &   0.271 &  0.271 &  0.333 &  0.251 &   0.239 &  0.26 &  - \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Dice similarity coefficients (top 10\%) for task and self-report data screening measures. Each entry corresponds to the Dice coefficient between two screening measures for the 10\% most suspicious participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. *Denotes statistical significance after correcting for multiple comparisons.}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccccc}
    \toprule
    {} &     INF &     ISD &     REL &    MAH &    READ &    VAR &     ACC &   WSLS & RT \\
    \midrule
    INF  &       - &         &         &        &         &        &         &        &    \\
    ISD  &  0.355* &       - &         &        &         &        &         &        &    \\
    REL  &  0.355* &  0.564* &       - &        &         &        &         &        &    \\
    MAH  &  0.355* &  0.667* &  0.359* &      - &         &        &         &        &    \\
    READ &  0.290* &   0.231 &   0.154 &  0.231 &       - &        &         &        &    \\
    VAR  &   0.116 &   0.080 &   0.080 &  0.160 &   0.133 &      - &         &        &    \\
    ACC  &  0.269* &   0.137 &   0.164 &  0.192 &   0.247 &  0.171 &       - &        &    \\
    WSLS &   0.242 &   0.103 &   0.154 &  0.205 &   0.231 &  0.240 &  0.630* &      - &    \\
    RT   &   0.164 &   0.105 &   0.132 &  0.184 &  0.289* &  0.164 &   0.225 &  0.237 &  - \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Dice similarity coefficients (top 25\%) for task and self-report data screening measures. Each entry corresponds to the Dice coefficient between two screening measures for the 25\% most suspicious participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. *Denotes statistical significance after correcting for multiple comparisons.}
\end{table}

@@

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccc}
    \toprule
    {} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
    \midrule
    Acc      &  -0.295* &  -0.166* &  -0.093* &  -0.134* &  -0.020 &  -0.051 &  -0.037 \\
    Pts      &  -0.225* &   -0.076 &   -0.023 &  -0.144* &  -0.061 &  -0.051 &   0.024 \\
    WS       &  -0.327* &  -0.160* &  -0.129* &  -0.171* &  -0.006 &  -0.048 &  -0.062 \\
    LS       &   0.285* &   0.158* &   0.146* &    0.050 &  -0.037 &   0.000 &  0.110* \\
    Pers     &   0.134* &    0.066 &    0.032 &   0.166* &   0.018 &   0.080 &  -0.004 \\
    $\beta$  &  -0.370* &  -0.157* &  -0.114* &  -0.185* &   0.017 &  -0.063 &  -0.043 \\
    $\eta_p$ &  -0.097* &  -0.105* &  -0.101* &   -0.033 &  -0.020 &  -0.015 &  -0.041 \\
    $\eta_n$ &   0.168* &   0.094* &   0.108* &   -0.050 &  -0.056 &  -0.020 &   0.042 \\
    $\kappa$ &  -0.175* &  -0.137* &  -0.147* &   -0.008 &  -0.020 &  -0.028 &  -0.061 \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman correlations between task behavior and self-report symptom measures when no screening and rejections have been applied. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

\begin{table}[H]
    \centering
    \small
    \begin{tabular}{rccccccc}
    \toprule
    {} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
    \midrule
    Acc      &  -0.263* &  -0.144* &  -0.105* &  -0.106* &  -0.009 &  -0.020 &  -0.033 \\
    Pts      &  -0.187* &   -0.042 &   -0.020 &  -0.126* &  -0.055 &  -0.028 &   0.036 \\
    WS       &  -0.291* &  -0.137* &  -0.123* &  -0.161* &  -0.019 &   0.006 &  -0.044 \\
    LS       &   0.314* &   0.170* &   0.156* &    0.034 &  -0.036 &  -0.037 &  0.124* \\
    Pers     &    0.083 &    0.022 &    0.011 &   0.151* &   0.010 &   0.076 &  -0.021 \\
    $\beta$  &  -0.332* &  -0.134* &  -0.109* &  -0.173* &   0.010 &  -0.040 &  -0.023 \\
    $\eta_p$ &   -0.056 &   -0.089 &  -0.105* &   -0.013 &  -0.029 &   0.034 &  -0.035 \\
    $\eta_n$ &   0.259* &   0.134* &   0.122* &   -0.021 &  -0.063 &   0.019 &   0.053 \\
    $\kappa$ &  -0.171* &  -0.125* &  -0.150* &   -0.016 &  -0.032 &  -0.033 &  -0.060 \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Spearman correlations between task behavior and self-report symptom measures after applying rejections based on choice accuracy (7\% of sample). Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. *Denotes statistical significance ($\alpha=0.05$, not corrected for multiple comparisons).}
\end{table}

>>>>

% load packages
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage{authblk}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{xr-hyper} % for cross-referencing between documents
\usepackage{hyperref}
\usepackage{float}
\usepackage{amsmath}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[flushmargin]{footmisc}
\usepackage[flushleft]{threeparttable}
\usepackage{array}
\usepackage[font=small, labelfont=it]{caption}
\usepackage{booktabs}
\usepackage{xcolor,soul}
\usepackage[export]{adjustbox}    % center wide tables on page

@@

\begin{figure}[h]
    \includegraphics[width=17cm]{../figures/supp_01.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Signed Spearman rank correlations between task behavior (y-axis) and symptom measures (x-axis) under different regimes of data screening and participant exclusions. (A) No Screening = no exclusions ($N=386$). (B) Accuracy Only = exclusions based on chance-level performance in the reversal-learning task ($N=352$). (C) Infrequency Only = exclusions based on invalid or improbable responses to infrequency items ($N=301$). (D) Both Types = exclusions based on the previous two measures ($N=283$). Only statistically significant correlations are shown ($p<0.05$ not corrected for multiple comparisons). Black Xs indicate significant correlations ablated under screening. Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
    \label{fig:correlations_s1}
\end{figure}

\clearpage
\subsection*{Bootstrapping Analysis}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_02.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{The pattern of significant behavior-symptom correlations before (A; $N=386$) and after (B; $N=301$) screening compared to the resulting pattern when random subsets of participants ($N=301$, matched to screening using the infrequency measure) are removed (C). Panels (A) and (B) are reproduced from Figure 4 for convenience. (C) The fraction of significant correlations in 5000 bootstrapped samples. (D) The similarity of the pattern of correlations after removal of random subsets to that before and after screening using the infrequency measure ($N=5000$ bootstrapped samples). Similarity was calculated using the simple matching coefficient. Random removal subsets were significantly more similar to the ``No Screening" than to the ``Infrequency" screening datasets (two-tailed, paired-samples $t$-test: $t = 262.490$, $p < 0.001$, $d = 3.713$, 95\% CI = [0.136, 0.138]).}
    \label{fig:random}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and false positive rates generalize to other sets of variables}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_03.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{False positive rates for spurious correlations \emph{increase} with sample size. \textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} False positive rates for inverse temperature ($\beta$) and depression scores (7-down) as a function of sample size and proportion of C/IE participants. False positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\beta$ and 7-down was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:bootstrap_s1}
\end{figure}

\clearpage
\subsection*{The relationship between sample size and true positive rates for true correlations}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_04.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{True correlations are independent of the proportion of C/IE participants in the sample. \textit{Left:} Spearman rank correlations and 95\% bootstrap confidence intervals between learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. The thick dashed lines indicate the threshold for statistical significance for the Spearman correlation at the corresponding sample size. Markers are jittered along the x-axis for legibility. \textit{Right:} True positive rates for learning rate asymmetry ($\kappa$) and anxiety scores (GAD-7) as a function of sample size and proportion of C/IE participants. True positive rate was calculated as the proportion of bootstrap samples in which the correlation between $\kappa$ and GAD-7 was statistically significant. The horizontal dotted line denotes the expected false positive rate at $\alpha = 0.05$.}
    \label{fig:bootstrap_s2}
\end{figure}

@@

\subsection*{Posterior predictive checks}
\begin{figure}[H]
    \includegraphics[width=16cm]{../figures/supp_05.png}
    \centering
    \captionsetup{width=0.88\textwidth}
    \caption{Posterior predictive checks for the risk-sensitive temporal difference learning model. (A) Observed (black) and predicted (blue) learning curves averaged across the group ($N=375$). (B) Observed versus predicted choice accuracy across participants ($N=375$). (C) Distribution of average predictive density across participants ($N=375$).}
    \label{fig:posterior_check}
\end{figure}

@@

\clearpage
\subsection*{Careless participants show different behaviors on the reversal learning task}
\begin{table}[H]
    \centering
    \begin{tabular}{lcccccc}
    \toprule
    {} &  Attentive &    C/IE &   $t$-value &   $p$-value &  Cohen's $D$ & 95\% CI \\
    \midrule
    Acc      &      0.587 &   0.532 &  4.008 &  $<$0.001 &  0.492 &    [0.028, 0.082] \\
    Pts      &     50.163 &  47.729 &  2.376 &     0.019 &  0.292 &    [0.426, 4.441] \\
    WS       &      0.898 &   0.776 &  5.387 &  $<$0.001 &  0.662 &    [0.077, 0.165] \\
    LS       &      0.609 &   0.751 & -5.335 &  $<$0.001 &  0.655 &  [-0.195, -0.090] \\
    Pers     &      0.245 &   0.259 & -1.505 &     0.139 &  0.185 &   [-0.033, 0.004] \\
    $\beta$  &      6.754 &   4.082 &  5.404 &  $<$0.001 &  0.664 &    [1.702, 3.640] \\
    $\eta_p$ &      0.643 &   0.551 &  2.846 &     0.007 &  0.350 &    [0.029, 0.157] \\
    $\eta_n$ &      0.738 &   0.784 & -1.516 &     0.120 &  0.186 &   [-0.106, 0.013] \\
    $\kappa$ &     -0.069 &  -0.218 &  3.729 &  $<$0.001 &  0.458 &    [0.071, 0.227] \\
    \bottomrule
    \end{tabular}
    \captionsetup{width=0.88\textwidth}
    \caption{Measures of task behavior compared between attentive ($N=301$) and C/IE ($N=85$) participants. Metrics compared using two-tailed, two-sample permutation $t$-test with $df=384$ ($\alpha = 0.05$, not corrected for multiple comparisons). Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry.}
\end{table}

@@

\begin{table}[H]
    \centering
    \begin{adjustbox}{center}
    \tiny
    \begin{tabular}{rccccccccc}
        \toprule
        {} &      INF &      ISD &      REL &      MAH &    READ &     VAR &     ACC &   WSLS & RT \\
        \midrule
        INF  &                           - &                             &                             &                          &                 &                 &                            &                 &    \\
    ISD  &   \textbf{0.337 ($<$0.001)} &                           - &                             &                          &                 &                 &                            &                 &    \\
    REL  &  \textbf{-0.360 ($<$0.001)} &  \textbf{-0.804 ($<$0.001)} &                           - &                          &                 &                 &                            &                 &    \\
    MAH  &   \textbf{0.406 ($<$0.001)} &   \textbf{0.836 ($<$0.001)} &  \textbf{-0.608 ($<$0.001)} &                        - &                 &                 &                            &                 &    \\
    READ &              -0.111 (0.644) &   \textbf{0.209 ($<$0.001)} &     \textbf{-0.193 (0.002)} &            0.138 (0.220) &               - &                 &                            &                 &    \\
    VAR  &              -0.061 (1.000) &              -0.038 (1.000) &               0.068 (0.999) &           -0.024 (1.000) &  -0.026 (1.000) &               - &                            &                 &    \\
    ACC  &  \textbf{-0.206 ($<$0.001)} &              -0.133 (0.273) &               0.044 (1.000) &  \textbf{-0.182 (0.009)} &  -0.074 (0.996) &   0.027 (1.000) &                          - &                 &    \\
    WSLS &               0.060 (1.000) &               0.103 (0.794) &              -0.085 (0.971) &            0.115 (0.574) &   0.103 (0.790) &  -0.060 (1.000) &  \textbf{0.221 ($<$0.001)} &               - &    \\
    RT   &               0.040 (1.000) &              -0.025 (1.000) &               0.017 (1.000) &            0.013 (1.000) &  -0.158 (0.067) &  -0.007 (1.000) &             -0.094 (0.910) &  -0.050 (1.000) &  - \\
        \bottomrule
    \end{tabular}
    \end{adjustbox}
    \caption{Spearman rank correlations ($p$-value) of task and self-report data screening measures ($N=386$). Each entry corresponds to the Spearman correlation between two screening measures. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, corrected for multiple comparisons).}
\end{table}

\begin{table}[H]
    \centering
    \begin{adjustbox}{center}
    \tiny
    \begin{tabular}{rccccccccc}
        \toprule
        {} &     INF &     ISD &     REL &    MAH &   READ &    VAR &     ACC &  WSLS & RT \\
        \midrule
        INF  &                          - &                            &                            &                &                &                &                            &                &    \\
    ISD  &  \textbf{0.462 ($<$0.001)} &                          - &                            &                &                &                &                            &                &    \\
    REL  &  \textbf{0.484 ($<$0.001)} &  \textbf{0.691 ($<$0.001)} &                          - &                &                &                &                            &                &    \\
    MAH  &  \textbf{0.516 ($<$0.001)} &  \textbf{0.732 ($<$0.001)} &  \textbf{0.619 ($<$0.001)} &              - &                &                &                            &                &    \\
    READ &              0.319 (0.688) &              0.165 (1.000) &              0.165 (1.000) &  0.216 (1.000) &              - &                &                            &                &    \\
    VAR  &              0.208 (1.000) &              0.216 (1.000) &              0.238 (1.000) &  0.259 (1.000) &  0.292 (0.981) &              - &                            &                &    \\
    ACC  &     \textbf{0.379 (0.011)} &              0.312 (0.792) &              0.258 (1.000) &  0.344 (0.180) &  0.237 (1.000) &  0.282 (0.998) &                          - &                &    \\
    WSLS &              0.253 (1.000) &              0.247 (1.000) &              0.227 (1.000) &  0.258 (1.000) &  0.299 (0.964) &  0.303 (0.901) &  \textbf{0.505 ($<$0.001)} &              - &    \\
    RT   &              0.267 (1.000) &              0.219 (1.000) &              0.271 (1.000) &  0.271 (1.000) &  0.333 (0.363) &  0.251 (1.000) &              0.239 (1.000) &  0.260 (1.000) &  - \\
        \bottomrule
    \end{tabular}
    \end{adjustbox}
    \caption{Dice similarity coefficients ($p$-value) for task and self-report data screening measures for the top 10\% most suspicious participants. Each entry corresponds to the Dice coefficient between two screening measures for the 10\% most suspicious participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. Bolded entries indicate statistical significance for a two-sided Dice similarity permutation test ($\alpha = 0.05$, corrected for multiple comparisons).}
\end{table}

\begin{table}[H]
    \centering
    \begin{adjustbox}{center}
    \tiny
    \begin{tabular}{rccccccccc}
        \toprule
        {} &     INF &     ISD &     REL &    MAH &    READ &    VAR &     ACC &   WSLS & RT \\
        \midrule
        INF  &                          - &                            &                            &                &                         &                &                            &                &    \\
    ISD  &  \textbf{0.355 ($<$0.001)} &                          - &                            &                &                         &                &                            &                &    \\
    REL  &  \textbf{0.355 ($<$0.001)} &  \textbf{0.564 ($<$0.001)} &                          - &                &                         &                &                            &                &    \\
    MAH  &  \textbf{0.355 ($<$0.001)} &  \textbf{0.667 ($<$0.001)} &  \textbf{0.359 ($<$0.001)} &              - &                         &                &                            &                &    \\
    READ &     \textbf{0.290 (0.006)} &              0.231 (0.231) &              0.154 (0.999) &  0.231 (0.231) &                       - &                &                            &                &    \\
    VAR  &              0.116 (1.000) &              0.080 (1.000) &              0.080 (1.000) &  0.160 (0.996) &           0.133 (1.000) &              - &                            &                &    \\
    ACC  &     \textbf{0.269 (0.020)} &              0.137 (1.000) &              0.164 (0.985) &  0.192 (0.809) &           0.247 (0.088) &  0.171 (0.968) &                          - &                &    \\
    WSLS &              0.242 (0.121) &              0.103 (1.000) &              0.154 (0.999) &  0.205 (0.635) &           0.231 (0.231) &  0.240 (0.140) &  \textbf{0.630 ($<$0.001)} &              - &    \\
    RT   &              0.164 (0.988) &              0.105 (1.000) &              0.132 (1.000) &  0.184 (0.879) &  \textbf{0.289 (0.007)} &  0.164 (0.985) &              0.225 (0.307) &  0.237 (0.162) &  - \\
        \bottomrule
    \end{tabular}
    \end{adjustbox}
    \caption{Dice similarity coefficients ($p$-value) for task and self-report data screening measures for the top 25\% most suspicious participants. Each entry corresponds to the Dice coefficient between two screening measures for the 25\% most suspicious participants. Acronyms: INF = infrequency item; ISD = inter-item standard deviation; REL = personal reliability; MAH = Mahalanobis distance; READ = reading time; VAR = choice variability; ACC = choice accuracy; WSLS = win-stay lose-shift rate; RT = suspicious response times. Bolded entries indicate statistical significance for a two-sided Dice similarity permutation test ($\alpha = 0.05$, corrected for multiple comparisons).}
\end{table}

@@

\begin{table}[H]
    \centering
    \begin{adjustbox}{center}   
    \scriptsize
    \begin{tabular}{rccccccc}
        \toprule
        {} &       7u &       7d &    GAD-7 &      BIS &     BAS &   SHAPS &    PSWQ \\
        \midrule
        Acc      &  \textbf{-0.295 ($<$0.001)} &     \textbf{-0.166 (0.001)} &  \textbf{-0.093 (0.041)} &     \textbf{-0.134 (0.006)} &  -0.020 (0.328) &  -0.051 (0.158) &          -0.037 (0.232) \\
    Pts      &  \textbf{-0.225 ($<$0.001)} &              -0.076 (0.065) &           -0.023 (0.315) &     \textbf{-0.144 (0.003)} &  -0.061 (0.104) &  -0.051 (0.154) &           0.024 (0.321) \\
    WS       &  \textbf{-0.327 ($<$0.001)} &  \textbf{-0.160 ($<$0.001)} &  \textbf{-0.129 (0.009)} &  \textbf{-0.171 ($<$0.001)} &  -0.006 (0.449) &  -0.048 (0.178) &          -0.062 (0.116) \\
    LS       &   \textbf{0.285 ($<$0.001)} &   \textbf{0.158 ($<$0.001)} &   \textbf{0.146 (0.002)} &               0.050 (0.157) &  -0.037 (0.241) &   0.000 (0.494) &  \textbf{0.110 (0.015)} \\
    Pers     &      \textbf{0.134 (0.004)} &               0.066 (0.111) &            0.032 (0.271) &   \textbf{0.166 ($<$0.001)} &   0.018 (0.370) &   0.080 (0.064) &          -0.004 (0.469) \\
    $\beta$  &  \textbf{-0.370 ($<$0.001)} &  \textbf{-0.157 ($<$0.001)} &  \textbf{-0.114 (0.019)} &  \textbf{-0.185 ($<$0.001)} &   0.017 (0.377) &  -0.063 (0.105) &          -0.043 (0.204) \\
    $\eta_p$ &     \textbf{-0.097 (0.037)} &     \textbf{-0.105 (0.023)} &  \textbf{-0.101 (0.029)} &              -0.033 (0.274) &  -0.020 (0.351) &  -0.015 (0.402) &          -0.041 (0.213) \\
    $\eta_n$ &   \textbf{0.168 ($<$0.001)} &      \textbf{0.094 (0.032)} &   \textbf{0.108 (0.016)} &              -0.050 (0.165) &  -0.056 (0.143) &  -0.020 (0.351) &           0.042 (0.205) \\
    $\kappa$ &  \textbf{-0.175 ($<$0.001)} &     \textbf{-0.137 (0.004)} &  \textbf{-0.147 (0.002)} &              -0.008 (0.444) &  -0.020 (0.356) &  -0.028 (0.294) &          -0.061 (0.118) \\
        \bottomrule
    \end{tabular}
    \end{adjustbox}
    \caption{Spearman rank correlation ($p$-value) between task behavior and self-report symptom measures when no screening and rejections have been applied ($N=386$). Acronyms: Acc = choice accuracy; Pts = total points earned; WS = win-stay rate; LS = lose-shift rate; Pers = perseveration errors; $\beta$ = inverse temperature; $\eta_p$ = positive learning rate; $\eta_n$ = negative learning rate; $\kappa$ = learning rate asymmetry. Bolded entries indicate statistical significance for a two-sided rank correlation test ($\alpha = 0.05$, not corrected for multiple comparisons).}
\end{table}
